
---
title: "FARSr: A Package for Traffic Accident Data Analysis in the US."
author: "Yi Xiong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Traffic Accident Data Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Functions

This package includes some useful function to analyze the data in FARS that were

- `fars_read`: Read data from FARS
- `make_filename`: Make file name with a given year
- `fars_read_years`: Read mulitple FARS data files
- `fars_map_state`: Visualize the accidents in the US map in a given year, state
- `fars_summarize_years`: Summarize the number of observations by year


# Read FARS Data

Through `fars_read`, we can read the FARS data that was saved by csv file with ".bz2" extension. 

```{r}
library(FARSr)
file <- system.file("extdata", "accident_2015.csv.bz2", package = "FARSr")
data <- fars_read(file)
head(data)
```


# Summary of FARS Data

The `fars_summarize_years` can return the pivot table with the number of monthly accident cases (row) and the defined year(s) (column). Here the input parameter should be a numeric vector.

```{r}
setwd(system.file("extdata", package = "FARSr"))
fars_summarize_years(2013:2015)
```


# Visualization of accident locations

The `fars_map_state` returns a map with the plot of the state with accident locations. The State index was defined from 1 to 56.

```{r}
setwd(system.file("extdata", package = "FARSr"))
unique(data$STATE) # 56
par(mfrow = c(1,3))
for (i in 2013:2015) {
  fars_map_state(50, i)
  mtext(paste(i))
}
```
